Simulating Dwarf Galaxy Evolution with Individual Star Feedback and Chemical Evolution

### 2018-02-15 main.tex
completed revisions of sections 4 and 5.

These large metal mass loading factors indicate that a majority of the metals produced in our dwarf galaxy are ejected from the disk. This is quantified in the lower panel of Fig.~\ref{fig:metal_evolution}, where we show the mass fraction of metals in the disk, CGM, and outside the virial radius of our galaxy over time. After the first 20 Myr, supernova-driven winds rapidly drive out large quantities of metals from the disk and into the galaxy's halo. This continues throughout the simulation, with only $\sim$12\% of produced metals residing in the disk of the galaxy. It only takes 150 Myr for some metals to reach the virial radius of the halo, with a steadily increasing fraction continually leaving the virial radius, reaching 40\% by the end of the simulation. Likewise, the CGM metal content continually decreases until the end of the simulation, from loss through the virial radius of the halo. Although the metal content of the ISM gradually decreases throughout the simulation, it seems somewhat steady at $\sim 10\%$ through the final 200~Myr of evolution. See Section~\ref{sec:obs_metals} for further discussion.
%\textbf{closing sentence}

@@

The observational sample of isolated, gaseous, low mass dwarf galaxies is limited compared to more massive galaxies, but has improved substantially with recent blind and targeted \ion{H}{1} surveys \citep[e.g.][]{Giovanelli2005, Geha2006, Geha2012, Walter2008, Cannon2011, Haynes2011, Hunter2012, Bradford2015, James2015, Tollerud2015, Sand2015, Wang2017}. However, the sample of isolated, gaseous dwarf galaxies with $M_{*} < 10^{7}$~M$_{\odot}$ remains small. In Figure ~\ref{fig:KS} we show where our galaxy lies relative to the observed Kennicutt-Schmidt (KS) relation (left) for low mass galaxies, and the extended Schmidt law (ESL) (right). In both diagrams, our simulations are given by the colored points, sampled every 1 Myr throughout the entire simulation. Although simple to measure in simulations, these quantities are challenging to directly compare to observations. We have attempted to make a reasonable analog to how $\Sigma_{\rm sfr}$ and $\Sigma_{\rm gas}$ are measured observationally for low mass dwarfs given the procedure described in \citet{Roychowdhury2014}. We define $\Sigma_{\rm sfr} = \dot{M}_{*, \rm{10 Myr}} / A_{*, \rm{10 Myr}}$, where $\dot{M}_{*, \rm{10 Myr}}$ is the SFR measured over the preceding 10 Myr, and $A_{*, \rm{10 Myr}}$ is the disk defined out to the farthest star formed within the previous 10 Myr. Likewise, $\Sigma_{\rm gas} = M_{\rm gas, 10 Myr} / A_{*, \rm{10 Myr}}$, where M$_{\rm gas, 10 Myr}$ is the total gas mass within this defined disk. However, the total gas content cannot be determined observationally. To match this limitation, we follow \cite{Roychowdhury2014} and take $\Sigma_{\rm gas, obs} = 1.34 \times \Sigma_{\rm HI}$, where the factor 1.34 attempts to account for He. There is generally no correction applied to account for any H$_{2}$ or HII content. The molecular component is discussed further in Section~\ref{sec:molecular gas content}.

\begin{figure*}
\centering
\includegraphics[width=0.475\linewidth]{all_gas_schmidt_law_evolution}
\includegraphics[width=0.475\linewidth]{all_gass_efficiency_evolution}
\caption{The KS law (left) and ESL (right) relationships for our galaxy as measured every 1 Myr. We take $\Sigma_{\rm gas, obs} = 1.34 \times \Sigma_{\rm HI}$ in our simulations to make a fair comparison to the observational sample (see text for more details). Plotted as points on both plots are recent observations from the SHIELD sample \citep{Teich2016}. On the left, we also give the best fit line to galaxies from the FIGGS sample from \cite{Roychowdhury2014}, and on the right we also show the best fit line and 1 $\sigma$ errors from \cite{Shi2011}. The simulations points are colored by time, with dark / purple early and light / green late. This is simply to indicate there is no obvious correlation with time in this diagram.}
\label{fig:KS}
\end{figure*}

In both panels, we also include recent observational constraints on these relationships. For the KS relationship we include the best fit line from \citet{Roychowdhury2014} (black, dashed). In both we give recent measurements from the SHIELD galaxy sample \citep{Teich2016} (black, points). Recently, \cite{Roychowdhury2017} demonstrated that the best fit line in the ESL from \cite{Shi2011} extends to the low mass FIGGS sample of galaxies; we give this best fit line and 1$\sigma$ errors in the right hand panel (black lines). Our galaxy fluctuates significantly about both relationships with no clear trends in time. However, in both cases, it is consistent with the available observational sample. At times our galaxy exhibits gas surface densities below the observational constraints. The trend is still consistent with higher densities at this point, but with a larger scatter towards lower star formation rate densities and efficiencies.

Fig.~\ref{fig:KS} represents a remarkable result. In constructing our galaxy model, we employed \textit{no} tuning of the underlying physics, adopting only canonical values for any available free parameters. It is non-trivial that our galaxy should oscillate about the median relationships in Fig.~\ref{fig:KS}, but signifies a proper accounting of the relevant physics governing gas and star forming properties in our galaxy. This result is consistent with recent galactic evolution simulations run at high resolution with a detailed accounting of stellar feedback physics (\textit{relevant citations})
%mm 
%ae: but does this bit then contradict my statement that this is remarkable? if its 'just gravity' at play?
   but also with the demonstration by \citet{Li2005} that the KS law can be reproduced 
   by gravitation acting on an isothermal disk, which was argued to demonstrate that 
   this represents the basic physics at work.

@@

Interestingly, in this low-dust regime, our H$_2$ formation is dominated by the gas-phase reactions H$^-$~+~H~$\rightarrow$~H$_2$~+~e$^{-}$. In our model, H$^{-}$ is produced solely through the reaction H~+~e$^{-} \rightarrow$ H$^{-}$~+~$\gamma$. Prior to the establishment of a local stellar radiation field, e$^{-}$ production is dominated by the ionizations of H and He from the UVB. This has the seemingly counterintuitive effect that turning off the UVB actually decreases the formation rate of H$_2$, as confirmed in test simulations. In a test simulation ignoring H$^{-}$, we find H$_{2}$ mass fractions on order of  $\sim 5\%$ by first star formation, a factor of 3 reduction from our fiducial model.

This explains our contention with the simulations in \citet{Hu2016} and \citet{Hu2017}, which find low molecular fractions ($f_{\rm H_2} \sim 10^{-4}$) even in their simulations without any feedback ($f_{\rm H_2} \sim 2 \times 10^{-3}$). Although these works do contain a non-equilibrium chemical model, they do not include either H$^{-}$ or a background radiation field. Our model suggests that H$^{-}$ and a UVB (in the absence of a local radiation field) are critical components in H$_2$ formation in small dwarf galaxies. It is not surprising that the gas phase reactions dominate over grain catalysis in this low metallicity regime \citep{Glover2003}, but the total amount of H$_2$ formed is perhaps surprising. However, the rate coefficients association with gas-phase H$_2$ formation are uncertain by an order of magnitude \citep{Glover2006,Glover2007}.
%In addition, \cite{Glover2006} demonstrated that the total amount of H$_2$ formed can be quite sensitive to the initial conditions.
Finally, our model lacks additional chemistry which may be important in the formation and destruction of H$_2$, including HD chemistry, C and O chemistry, a detailed dust model, and cosmic rays. It is unclear how the combination of all of these effects will behave, especially considering that even at this resolution, we are unable to resolve the high density turbulent density perturbations in which H$_2$ forms most efficiently \citep{Glover2007}. This uncertainty certainly warrants further study of molecular gas in low metallicity dwarf galaxies.
%ae rewrote above and took out this citation, need to see if need to put back in:
%            there is some possible observational evidence for higher than expected ($\sim 15$ \%)   %            molecular fractions \citep{Schruba2017}, though this still remains highly uncertain.

@@

The simulations presented here have not yet been run for the gigayear timescales required to make direct comparisons to the observed stellar and gas phase metallicities of comparable dwarf galaxies at $z = 0$. However, we can compare to a key observable, the retention fraction of metals within stars and the galaxy's ISM compared to what would be expected from stellar evolution models based on the galaxy's star formation history. This can be done readily with Milky Way dSph's, whose stars seem to retain very little of the expected metal production: on order of a few percent or less depending on the galaxy and the species \citep{Kirby2011-metals}. However, environmental effects, namely ram pressure and tidal stripping, complicate the understanding of how these metals were removed from the galaxy.

Leo P, the dwarf galaxy we approximate in our initial conditions, is extremely valuable as a gaseous, star forming low-mass dwarf galaxy, with an observable \ion{H}{2} region, necessary for determining gas phase abundances, and close enough to the Milky Way to conduct this experiment. Leo P retains $\sim$ 5\% $\pm$ 2\% of its metals, $\sim$ 1\% in stars and the remaining in ISM gas \citep{McQuinn2015}. As discussed in Section~\ref{sec:chemical evolution}, roughly 90\% of the tracked metals produced during the simulation no longer reside within the galaxy's disk. At the end of our simulation, we agree with the observations; however, this is an evolving quantity that also depends on how much (if any) subsequent re-accretion of these metals occurs. Although more than half of these metals are expected to eventually re-accrete \citep{Angles-Alcazar2017}, it is still possible that
most of the metals that have been produced at these early times will remain outside the galaxy disk. We will examine the long term, and species-by-species, evolution of the metal retention fraction in future work.

It is interesting to consider whether ejected metals in our model reside in the CGM or have been ejected into the IGM. While this cannot be observationally determined for dwarf galaxies at this mass, cosmological simulations of a $M_{\rm vir} = 10^{10}$ M$_{\odot}$ galaxy show that, by redshift zero $\sim$ 60\% of ejected gas is recycled, while 40\% is ejected from the galaxy's halo \citep{Angles-Alcazar2017}. In our case, no metals have been ejected beyond the virial radius; this is not surprising however, given that metals ejected beyond the halo would need to travel with an average velocity of 150 km s$^{-1}$ for the entirety of our simulation time.  We find 13.7\% of all metals lie within 1 kpc of the center of our galaxy, 26.5\% within 0.25 $R_{\rm vir}$ (or 6.85 kpc), and 38.6\% outside $R_{\rm vir}$. The re-accretion or final ejection of this gas is directly relevant to the chemical evolution of low mass dwarf galaxies. Recycling of metal enriched gas could be a significant driver of long-term chemical evolution in low mass galaxies, particularly if a majority of metals ejected from the disk (itself nearly all the metals produced by the galaxy) return. Our model seems to suggest that many of the metals ejected into the halo will not be recycled back into the galaxy, but this is difficult to determine with only 500~Myr of evolution. In addition, the accretion of pristine gas from the IGM could significantly affect the gas flows around the galaxy, possibly promoting the retention of ejected metals. This effect is not included in our isolated galaxy simulations, and its role is beyond the scope of this work.

\subsection{Missing Physics}
Although we include detailed physics in our simulations, there remains additional physical processes that may be relevant, these are discussed below.

\subsubsection{Full Stellar Wind Model}
\label{sec:stellar winds discussion}
Our stellar wind model significantly reduces the injected wind velocity from $\sim$1000 km s$^{-1}$ to 1 km s$^{-1}$. Although our model is capable of generating realistic stellar winds with temperature profiles and radial evolution comparable to those expected from analytic calculations \citep{Weaver1977}, the hot, fast winds place a near constant and severe constraint on the Courant time step that renders $\gtrsim$100~Myr simulations impractical. When considered in isolation, stellar winds are an important source of pre-SN feedback and do dramatically influence the dynamical evolution on molecular cloud and galaxy scales \citep{Dale2008,Peters2017,Gatto2017}. However, when considered together with ionizing radiation, stellar winds contain less total energy \citep{Agertz2013} and do not seem to have a significant dynamical influence in either idealized simulations \citep{Geen2015} or 
%mm GMCs
   individual giant molecular clouds
\citep{Dale2014}. They are even less relevant in the low-metallicity regime studied here, as stellar winds become weaker with decreasing metallicity \citep{Puls2000, Vink2005}. Although they likely have minimal dynamical importance
%mm 
   at resolutions where peak densities are not anyway high enough to trap ionization 
   fronts, 
a full model of stellar winds may affect detailed ISM properties and metal mixing, warranting a closer examination in a future work.

%old comment: (need to ref or back up this claim: see Dale et al. 2014 for individual clouds, while the right panel of Fig 2 in Shull \& Saken 1995 shows that the integrated wind energy from a cluster is about 10\% that of the supernovae -M).

\subsubsection{Cosmic Rays and Magnetic Fields}
Recent work has explored the importance of cosmic ray feedback in regulating the ISM and wind properties in galactic disks \citep{Hanasz2013,GirichidisCR,Simpson2016,Farber2017}, isolated galaxies \citep{SalemBryanCorlies,Salem2015,Pakmor2016,Ruszkowski2017}, and galaxies in cosmological context \citep{SalemBryanHummels}. These relativistic charged particles act as a source of non-thermal pressure support in the galaxy's ISM, capable of driving outflows at different velocities and containing different thermal phases than those driven through thermal feedback alone \citep{SalemBryanCorlies}. Modeling cosmic rays is challenging, however, as they encompass a wide range of energies (give range), with significant uncertainties in how they propagate through the ISM \citep[e.g.][]{Wiener2017}. Their propagation is often modeled as a diffusive process, but in truth this diffusion should vary depending on cosmic ray energy. In addition, cosmic rays couple effectively to the magnetic fields of galaxies, diffusing preferentially along structured magnetic field lines within the ISM. Modeling cosmic ray feedback completely requires both an accurate cosmic ray model and magnetohydrodynamics in order to capture the interplay of these two physical phenomena. Finally, including MHD presents additional difficulties in untangling the effects each individual feedback mechanism on galaxy chemodynamics.

@@

Roughly half of massive stars live in binary pairs. Their interactions, primarily through mass transfer, can significantly alter their radiation properties and lifetimes. This can change both how much and how long these stars emit ionizing radiation, an important source of stellar feedback, and where and when these stars explode as supernovae. This effect is rarely accounted for in galaxy evolution models, which are commonly based on calculations of single star evolution (e.g. STARBURST99), but could be significant. For example, \cite{Zapartas2017} finds that binarity extends the timescales over which core collapse supernovae occur from a given star formation event, from a maximum time of $\sim$ 50~Myr to $\sim$~200~Myr. Although they find only $\sim 15\%$ of core collapse supernovae explode after 50~Myr, this could still be an important effect. Properly accounting for the delay times due to variations in individual star lifetimes has already been shown to change the significance of feedback and influence galaxy metallicity properties \citep{Kimm2015}. Extending the lifetimes of these stars could increase the role of radiation feedback, however this may be less important as these additional photons are more likely to escape the galaxy \citep[e.g.][]{Ma2016-binary}. 
% does this affect yields??
% runaway stars

Since we model stars on a star-by-star basis, both of these effects could be reasonably accounted for by stochastically assigning binary star properties to some subset of our individual stars. This is beyond the scope of this project, but will be investigated in future works.

\section{Conclusion}
\label{sec:conclusion}
We have developed a new method for simulating galaxy evolution with detailed feedback and chemical enrichment. For the first time on galaxy scales, we simultaneously model multi-channel stellar feedback in detail, accounting for stellar winds, core collapse and Type Ia supernovae, ionizing radiation followed through radiative transfer, photoelectric heating, and Lyman-Werner radiation using individual star particles. This, coupled with the detailed chemistry and heating/cooling physics followed with \textsc{Grackle}, allows us to capture realistic galaxy evolution in detail. In this work, we apply these methods to simulate the evolution of an isolated, low mass dwarf galaxy modeled after the $z=0$ properties of the Leo P ultrafaint dwarf galaxy. We present an overview of the properties of this galaxy in this work.
% AE: mention companion paper here if publish at same time

For our simulated dwarf galaxy, we find:
\begin{enumerate}
\item Multi-channel feedback is effective in this galaxy in regulating star formation consistent with the KS relationship and extended Schmidt law in observed galaxies. See Figures~\ref{fig:sfr_mass_evolution} and \ref{fig:KS}.

\item This feedback drives large outflows ($\eta \sim 50$ at 0.25~R$_{\rm vir}$) with metal mass loading factors near unity. By mass, nearly all of this outflow is moving with velocities below 100 km~s$^{-1}$, but there is a significant tail towards velocities up to 1000 km s$^{-1}$ (Figure~\ref{fig:outflow_velocity}). This galaxy is consistent with observed metal retention fractions of UFD's, retaining only $\sim$10\% of metals in the disk. By the end of the simulation the remaining metals reside within the virial radius ($\sim$50\%) and $\sim$40\% are ejected outside the virial radius. The fraction in the disk remains fairly constant towards the end of the simulation, but the metals in the halo are still evolving. See Figures \ref{fig:mass_outflow}, \ref{fig:outflow_velocity}, and \ref{fig:metal_evolution}.

\item A thin, yet resolved, gas scale height ($\sim$~50~pc) beyond our stellar radius, with larger scale heights ($\sim 100 - 200$~pc) driven by feedback interior to the stellar radius. This is comparable to the resolution limit of the diffuse \ion{H}{1} in observed, gaseous UFDs. See Figure~\ref{fig:scale_height}.

\item The ISRF of our galaxy is highly varying in time by orders of magnitude, though is relatively uniform in space at any given time. It is unclear how important these fluctuations are as a source of feedback, or if the affect can simply be approximated with a time averaged radial profile. See Figures \ref{fig:ISRF} and \ref{fig:ISRF_2D}.

>>>>

These large metal mass loading factors indicate that a majority of the metals produced in our dwarf galaxy are ejected from the disk. This is quantified in the lower panel of Fig.~\ref{fig:metal_evolution}, where we show the mass fraction of metals in the disk, circumgalactic medium (CGM), and outside the virial radius of our galaxy over time. After the first 20 Myr, supernova-driven winds rapidly drive out large quantities of metals from the disk and into the galaxy's halo. This continues throughout the simulation, with only $\sim$12\% of produced metals residing in the disk of the galaxy. It only takes 150 Myr for some metals to reach the virial radius of the halo, with a steadily increasing fraction continually leaving the virial radius, reaching 40\% by the end of the simulation. Likewise, the CGM metal content continually decreases until the end of the simulation, from loss through the virial radius of the halo. Although the metal content of the ISM gradually decreases throughout the simulation, it seems somewhat steady at $\sim 10\%$ through the final 200~Myr of evolution. See Section~\ref{sec:obs_metals} for further discussion.
%\textbf{closing sentence}

@@

The observational sample of isolated, gaseous, low mass dwarf galaxies is limited compared to more massive galaxies, but has improved substantially with recent blind and targeted \ion{H}{1} surveys \citep[e.g.][]{Giovanelli2005, Geha2006, Geha2012, Walter2008, Cannon2011, Haynes2011, Hunter2012, Bradford2015, James2015, Tollerud2015, Sand2015, Wang2017}. However, the sample of isolated, gaseous dwarf galaxies with $M_{*} < 10^{7}$~M$_{\odot}$ remains small. In Figure ~\ref{fig:KS} we show where our galaxy lies relative to the observed Kennicutt-Schmidt (KS) relation and extended Schmidt law (ESL)  for low mass galaxies. In both diagrams, our simulations are given by the colored points, sampled every 1 Myr throughout the entire simulation. Although simple to measure in simulations, these quantities are challenging to directly compare to observations.

%mm [new para]
We have attempted to make a reasonable analog to how $\Sigma_{\rm sfr}$ and $\Sigma_{\rm gas}$ are measured observationally for low mass dwarfs using the procedure described in \citet{Roychowdhury2014}. We define $\Sigma_{\rm sfr} = \dot{M}_{*,10} / A_{*,10}$, where $\dot{M}_{*,10}$ is the SFR measured over the preceding 10~Myr, and $A_{*,10}$ is the
%mm2 disk defined out to the farthest
   area of the disk within the radius of the outermost 
star formed within the previous 10 Myr. Likewise, $\Sigma_{\rm gas} = M_{\rm gas,10} / A_{*,10}$, where M$_{\rm gas,10}$ is the total gas mass within this defined disk. However, the total gas content cannot be determined observationally. To match this limitation, we follow \cite{Roychowdhury2014} and take $\Sigma_{\rm gas, obs} = 1.34 \times \Sigma_{\rm HI}$, where the factor 1.34 attempts to account for He. There is generally no correction applied to account for any H$_{2}$ or \ion{H}{2} content. The molecular component is discussed further in Section~\ref{sec:molecular gas content}.

\begin{figure*}
\centering
\includegraphics[width=0.475\linewidth]{all_gas_schmidt_law_evolution}
\includegraphics[width=0.475\linewidth]{all_gass_efficiency_evolution}
\caption{The KS law (left) and ESL (right) relationships for our galaxy as measured every megayear, plotted as points colored by time, with dark / purple early and light / green late. 
%mm2 We take $\Sigma_{\rm gas, obs} = 1.34 \times \Sigma_{\rm HI}$ in our simulations to make a fair comparison to the observational sample (see text for more details)
    See text for details of the calculation.
Recent observations from the SHIELD sample \citep{Teich2016} are plotted as 
%mm2 points
    black points with error bars.
On the left, we also give the best fit line to galaxies from the FIGGS sample from \cite{Roychowdhury2014}, and on the right we also show the best fit line and 1 $\sigma$ errors from \cite{Shi2011}.
%mm2  This  is simply to indicate there 
   There
is no clear correlation with time in this diagram.}
\label{fig:KS}
\end{figure*}

%mm2 In both panels, we also 
   We
include recent observational constraints on these relationships
%mm2
    in Figure ~\ref{fig:KS}. 
%mm2 For the KS relationship we 
   These 
include the best-fit line from \citet{Roychowdhury2014}, 
%mm2 (black, dashed). In both we give recent measurements from
the SHIELD galaxy sample \citep{Teich2016}, 
%mm2 (black, points). Recently, \cite{Roychowdhury2017} demonstrated that the best fit line in the ESL from \cite{Shi2011} extends to the low mass FIGGS sample of galaxies; we give this best fit line and 1$\sigma$ errors in the right hand panel (black lines). 
  and the best-fit line with 1$\sigma$ errors from \citet{Shi2011}, which 
  \citet{Roychowdhury2017} demonstrated extends to the low mass FIGGS sample of galaxies.
Our galaxy fluctuates significantly about both relationships with no clear trends in time. However, in both cases, it is consistent with the available observational sample. At times our galaxy exhibits gas surface densities below the observational constraints. The trend is still consistent with higher densities at this point, but with a larger scatter towards lower star formation rate densities and efficiencies.

%mm2 Fig.~\ref{fig:KS} represents a remarkable result. 
In constructing our galaxy model, we employed \textit{no} tuning of the underlying physics, adopting only canonical values for any available free parameters. It is thus non-trivial that our galaxy should oscillate about the median relationships in Fig.~\ref{fig:KS}, and signifies a proper accounting of the relevant physics governing gas and star forming properties in our galaxy. This result is consistent with 
%mm2 recent 
galactic evolution simulations run at high resolution with a detailed accounting of stellar feedback physics (\textit{relevant citations}
%mm2
   starting with A. Kravtsov 2003, ApJ L.)
%mm 
%ae: but does this bit then contradict my statement that this is remarkable? if its 'just gravity' at play?  
%mm2: that's the question, isn't it?  maybe keep the description of the result, but remove the claim of remarkability, as I have edited to do?
   but also with the demonstration by \citet{Li2006} that the KS law can be reproduced 
   by gravitation acting on an isothermal disk, which was argued to demonstrate that 
   this represents the basic physics at work.

@@

Interestingly, in this low-dust regime, our H$_2$ formation is dominated by the gas-phase reaction H$^-$~+~H~$\rightarrow$~H$_2$~+~e$^{-}$. In our model, H$^{-}$ is produced solely through the reaction H~+~e$^{-} \rightarrow$ H$^{-}$~+~$\gamma$. Prior to the establishment of a local stellar radiation field, e$^{-}$ production is dominated by the ionization of H and He from the ultraviolet background. This has the seemingly counterintuitive effect that turning off the ultraviolet background actually decreases the formation rate of H$_2$, as confirmed in test simulations. In a test simulation ignoring H$^{-}$, we find H$_{2}$ mass fractions on order of  $\sim 5\%$ by first star formation, a factor of 3 reduction from our fiducial model.

This explains our 
%mm2 contention 
    disagreement
with the simulations in \citet{Hu2016} and \citet{Hu2017}, which find low molecular fractions ($f_{\rm H_2} \sim 10^{-4}$) even in their simulations without any feedback ($f_{\rm H_2} \sim 2 \times 10^{-3}$). Although these works do contain a non-equilibrium chemical model, they do not include either H$^{-}$ or a background radiation field. Our model suggests that H$^{-}$ and the ultraviolet background (in the absence of a local radiation field) are critical components in H$_2$ formation in small dwarf galaxies. It is not surprising that the gas phase reactions dominate over grain catalysis in this low metallicity regime \citep{Glover2003}, but the total amount of H$_2$ formed is perhaps surprising. However, the rate coefficients associated with gas-phase H$_2$ formation are uncertain by an order of magnitude \citep{Glover2006,Glover2007}.
%In addition, \cite{Glover2006} demonstrated that the total amount of H$_2$ formed can be quite sensitive to the initial conditions.
%mm2 Finally, our model lacks additional chemistry which 
    Our model does lack additional chemistry that
may be important to the formation and destruction of H$_2$, including HD chemistry, C and O chemistry, a detailed dust model, and cosmic rays. It is unclear how the combination of all of these effects will behave, especially considering that even at this resolution, we are unable to resolve the high density turbulent density perturbations in which H$_2$ forms most efficiently \citep{Glover2007}. This uncertainty certainly warrants further study of molecular gas in low metallicity dwarf galaxies.
%ae rewrote above and took out this citation, need to see if need to put back in:
%            there is some possible observational evidence for higher than expected ($\sim 15$ \%)   %            molecular fractions \citep{Schruba2017}, though this still remains highly uncertain.

@@

The simulations presented here have not yet been run for the gigayear timescales required to make direct comparisons to the observed stellar and gas phase metallicities of comparable dwarf galaxies at $z = 0$. However, we can compare to a key observable, the retention fraction of metals within stars and the galaxy's ISM compared to what would be expected from
%mm2
  closed box
stellar evolution models based on the galaxy's star formation history. This can be done readily with Milky Way dSph's. Their stars seem to retain very little of the expected metal production: on order of a few percent or less depending on the galaxy and the species \citep{Kirby2011-metals}. However, environmental effects, namely ram pressure and tidal stripping, complicate the understanding of how these metals were removed from the galaxy.

Leo P, the dwarf galaxy we approximate in our initial conditions, is extremely valuable as a %mm2 gaseous, 
   gas-containing,
star forming, low-mass dwarf galaxy, with an observable \ion{H}{2} region, necessary for determining gas phase abundances, that is close enough to the Milky Way to conduct this experiment. Leo P retains $\sim$ 5\% $\pm$ 2\% of its metals, $\sim$ 1\% in stars and the rest in ISM gas \citep{McQuinn2015}. As discussed in Section~\ref{sec:chemical evolution}, roughly 90\% of the tracked metals produced during our simulation no longer reside within the galaxy's disk. At the end of our simulation, we 
%mm2
   thus
agree with the observations; however, this is an evolving quantity that also depends on how much (if any) subsequent re-accretion of these metals occurs. Although more than half of these metals are expected to eventually re-accrete \citep{Angles-Alcazar2017}, it is still possible that
most of the metals that have been produced at these early times will remain outside the galaxy disk. We will examine the long term, and species-by-species, evolution of the metal retention fraction in future work.

It is interesting to consider whether ejected metals in our model reside in the CGM or have been ejected into the intergalactic medium. While this cannot be observationally determined for dwarf galaxies at this mass, cosmological simulations of a $M_{\rm vir} = 10^{10}$ M$_{\odot}$ galaxy show that, by redshift zero $\sim$ 60\% of ejected gas is recycled, while 40\% is ejected from the galaxy's halo \citep{Angles-Alcazar2017}. In our case, no metals have been ejected beyond the virial radius; this is not surprising however, given that metals ejected beyond the halo would need to travel with an average velocity of 150 km s$^{-1}$ for the entirety of our simulation time.  We find 13.7\% of all metals lie within 1 kpc of the center of our galaxy, 26.5\% within 0.25 $R_{\rm vir}$ (or 6.85 kpc), and 38.6\% outside $R_{\rm vir}$.

%mm2 [new para]
The re-accretion or final ejection of this gas is directly relevant to the chemical evolution of low mass dwarf galaxies. Recycling of metal enriched gas could be a significant driver of long-term chemical evolution in low mass galaxies, particularly if a majority of metals ejected from the disk (itself nearly all the metals produced by the galaxy) return. Our model seems to suggest that many of the metals ejected into the halo will not be recycled back into the galaxy, but this is difficult to determine with only 500~Myr of evolution. In addition, the accretion of pristine gas from the intergalactic medium could significantly affect the gas flows around the galaxy, possibly promoting the retention of ejected metals. This effect is not included in our isolated galaxy simulations, and its role is beyond the scope of this work.

\subsection{Missing Physics}
Although we include many detailed physical models in our simulations, there remain additional physical processes that may be relevant, which we now discuss.

\subsubsection{Full Stellar Wind Model}
\label{sec:stellar winds discussion}
Our stellar wind model significantly reduces the injected wind velocity from $\sim$1000 km s$^{-1}$ to 1 km s$^{-1}$. Although our model is capable of generating realistic stellar winds with temperature profiles and radial evolution comparable to those expected from analytic calculations \citep{Weaver1977}, the hot, fast winds place a near constant and severe constraint on the Courant time step that renders $\gtrsim$100~Myr simulations impractical. When considered in isolation, stellar winds are an important source of pre-SN feedback and do dramatically influence the dynamical evolution on molecular cloud and galaxy scales \citep{Dale2008,Peters2017,Gatto2017}. However, when considered together with ionizing radiation, stellar winds contain less total energy \citep{Agertz2013} and do not seem to have a significant dynamical influence in either idealized simulations \citep{Geen2015} or 
%mm GMCs
   individual giant molecular clouds
\citep{Dale2014}. They are even less relevant in the low-metallicity regime studied here, as stellar winds become weaker with decreasing metallicity \citep{Puls2000, Vink2005}. Although they likely have minimal dynamical importance
%mm 
   at resolutions where peak densities are not anyway high enough to trap ionization 
   fronts, 
a full model of stellar winds may affect detailed ISM properties and metal mixing, warranting a closer examination in a future work.
%mm2: should we recover the reference to Shull \& Saken?
%old comment: (need to ref or back up this claim: see Dale et al. 2014 for individual clouds, while the right panel of Fig 2 in Shull \& Saken 1995 shows that the integrated wind energy from a cluster is about 10\% that of the supernovae -M).

\subsubsection{Cosmic Rays} 
%mm2 and Magnetic Fields}  One could make the case that we should have a separate discussion of magnetic fields.  However, this section is only about CRs.

Recent work has explored the importance of cosmic ray feedback in regulating the ISM and wind properties in galactic disks \citep{Hanasz2013,GirichidisCR,Simpson2016,Farber2017}, isolated galaxies \citep{SalemBryanCorlies,Salem2015,Pakmor2016,Ruszkowski2017}, and galaxies in cosmological context \citep{SalemBryanHummels}. These relativistic charged particles act as a source of non-thermal pressure support in the galaxy's ISM, capable of driving outflows at different velocities and containing different thermal phases than those driven through thermal feedback alone \citep{SalemBryanCorlies}. Modeling cosmic rays is challenging, however, as they encompass a wide range of energies,
%mm2 (give range), with 
   and there are
significant uncertainties in how they propagate through the ISM \citep[e.g.][]{Wiener2017}. Their propagation is often modeled as a diffusive process, but in truth this diffusion should vary depending on cosmic ray energy. In addition, cosmic rays couple effectively to the magnetic fields of galaxies, diffusing preferentially along structured magnetic field lines within the ISM. Modeling cosmic ray feedback completely thus requires both an accurate cosmic ray model and magnetohydrodynamics in order to capture the interplay of these two physical phenomena. Finally, including MHD presents additional difficulties in untangling the effects of each individual feedback mechanism on galaxy chemodynamics.

@@

Roughly half of massive stars live in binary pairs 
%mm2 doi:10.1051/0004-6361/201219621
   \citep{Sana2012}. 
Their interactions, primarily through mass transfer, can significantly alter their radiation properties and lifetimes. This can change both how much and how long these stars emit ionizing radiation, an important source of stellar feedback, and where and when these stars explode as supernovae. This effect is rarely accounted for in galaxy evolution models, which are commonly based on calculations of single star evolution (e.g. STARBURST99), but could be significant. For example, \citet{Zapartas2017} finds that binarity extends the timescales over which core collapse supernovae occur from a given star formation event, from a maximum time of $\sim$ 50~Myr to $\sim$~200~Myr. Although they find only $\sim 15\%$ of core collapse supernovae explode after 50~Myr, this could still be an important effect. Properly accounting for the delay times due to variations in individual star lifetimes has already been shown to change the significance of feedback and influence galaxy metallicity properties \citep{Kimm2015}. Extending the lifetimes of these stars could increase the role of radiation feedback, however this may be less important as these additional photons are more likely to escape the galaxy \citep[e.g.][]{Ma2016-binary}. 
% does this affect yields??
% runaway stars

Since we model stars on a star-by-star basis, both of these effects could be reasonably accounted for by stochastically assigning binary star properties to some subset of our individual stars. This is beyond the scope of this project, but will be investigated in future work.

\section{Conclusion}
\label{sec:conclusion}
We have developed a new method for simulating galaxy evolution with detailed feedback and chemical enrichment. For the first time on galaxy scales, we simultaneously model multi-channel stellar feedback in detail, accounting for stellar winds, core collapse and Type Ia supernovae, ionizing radiation followed through radiative transfer, photoelectric heating, and Lyman-Werner radiation using individual star particles. This, coupled with the detailed chemistry and heating/cooling physics followed with \textsc{Grackle}, allows us to capture realistic galaxy evolution in detail. In this work, we apply these methods to simulate the evolution of an isolated, low-mass, dwarf galaxy modeled after the $z=0$ properties of the Leo P ultrafaint dwarf galaxy. We present an overview of the properties of this 
%mm2 galaxy
    simulation 
in this work.
% AE: mention companion paper here if publish at same time

For our simulated dwarf galaxy, we find:
\begin{enumerate}
\item Multi-channel feedback is effective in this galaxy in regulating star formation 
%mm2 
   to occur at a rate 
consistent with the KS relationship and extended Schmidt law in observed galaxies. See Figures~\ref{fig:sfr_mass_evolution} and \ref{fig:KS}.

\item This feedback drives large outflows 
%mm2 ($\eta \sim 50$ at 0.25~R$_{\rm vir}$) with
   having mass loading factors of $\eta \sim 50$ at 0.25~R$_{\rm vir}$, and
metal mass loading factors near unity. By mass, nearly all of this outflow is moving with velocities below 100 km~s$^{-1}$, but there is a significant tail towards velocities up to 1000 km s$^{-1}$ (Figure~\ref{fig:outflow_velocity}).

%mm2 [made this a separate item]
\item 
%mm2 This galaxy result is consistent with the observed metal retention fractions of ultrafaint dwarfs, retaining only $\sim$10\% of metals in the disk. 
    Only $\sim$10\% of metals are retained in the disk of our simulated galaxy, consistent with the observed metal retention fractions of ultrafaint dwarfs.  By the end of the simulation $\sim$50\% of the remaining metals remain within the virial radius and $\sim$40\% 
have been ejected beyond the virial radius. The fraction in the disk remains fairly constant towards the end of the simulation, but the metals in the halo are still evolving. See Figures \ref{fig:mass_outflow}, \ref{fig:outflow_velocity}, and \ref{fig:metal_evolution}.

\item A thin, yet resolved, gas scale height ($\sim 50$~pc) beyond our stellar radius, with larger scale heights ($\sim 100$--200~pc) driven by feedback interior to the stellar radius. This is comparable to the resolution limit of the diffuse \ion{H}{1} in observed, gaseous ultrafaint dwarfs. See Figure~\ref{fig:scale_height}.

\item The ISRF of our galaxy is highly varying in time, by orders of magnitude, though it is relatively uniform in space at any given time. It is unclear how important these fluctuations are as a source of feedback, or if the affect can 
%mm2 simply 
be approximated with a time averaged radial profile. See Figures \ref{fig:ISRF} and \ref{fig:ISRF_2D}.
